---
title: "API Testing"
output: html_notebook
---

## Introduction

This notebook is testing whether or not we can pull congressional trade data from an API for free. We'll test the following websites:

- [FMP](https://site.financialmodelingprep.com/)
  - [Documentaion Here](https://site.financialmodelingprep.com/developer/docs#senate)
- [Finnhub](https://finnhub.io/)
  - [Documentaion Here](https://finnhub.io/docs/api/congressional-trading)
- [Benzinga APIs](https://www.benzinga.com/apis/)
  - [Documentaion Here](https://www.benzinga.com/apis/cloud-product/government-trades/)
- [House Stock Watcher](https://housestockwatcher.com/)
  - [Documentaion Here](https://housestockwatcher.com/api)

```{r Libraries + API Keys}
# load libraries
library(httr)
library(dotenv)
library(jsonlite)

# load .env file
load_dot_env("../.env")

# read in API Keys
fmp_api_key <- Sys.getenv("FMP_API_KEY")
finnhub_api_key <- Sys.getenv("FINNHUB_API_KEY")
benzinga_api_key <- Sys.getenv("BENZINGA_API_KEY")
```

### Test FMP

```{r}
headers = c(`Upgrade-Insecure-Requests` = '1')
params = list(`datatype` = 'json')

# url for senate trading api by stock
trades_url <- sprintf('https://financialmodelingprep.com/api/v4/senate-trading?symbol=AAPL&apikey=%s', fmp_api_key)
# url for senate disclosure rss feed
rss_url <- sprintf('https://financialmodelingprep.com/api/v4/senate-disclosure-rss-feed?page=0&apikey=%s', fmp_api_key)

# this one is not available under the free subscription pland
# response <- GET(trades_url , add_headers(.headers=headers), query = params)

# this one is not available under the free subscription plan
response <- GET(rss_url , add_headers(.headers=headers), query=params)

print(response)
```
### Test Finnhub

```{r}
url <- sprintf('https://finnhub.io/api/v1/stock/congressional-trading?symbol=AAPL&token=%s', finnhub_api_key)

response <- GET(url)

# returning 401 unauthorized error so probably can't use this one either
print(response)
```

### Test Benzinga

```{r}
url <- "https://api.benzinga.com/api/v1/gov/usa/congress/trades"
params <- list(token=benzinga_api_key)

response <- GET(url, query=query_params)

# returning 401 unauthorized error so probably can't use this one either
print(response)
```
Even though I can't seem to pull the data via API I can get a response from [here](https://docs.benzinga.com/benzinga-apis/government-trades/get-trades) in the browser using the API token. Can always use the browser to manually pull data if needed.

### Test House Stock Watcher

```{r}
url <- "https://house-stock-watcher-data.s3-us-west-2.amazonaws.com/data/all_transactions.json"
  
response <- GET(url)

data <- fromJSON(content(response, as = "text", encoding = "UTF-8"))

head(data)
```
This one seems to work and also has an option to do a manual download via the browser. 